Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-05 sections/background.tex
woah
Update on Overleaf.
small fixes

\section{Background}
\subsection{Looplets}
Finch represents iteration patterns using Looplets, a language that decomposes datastructure iterators hierarchically. 
%
Looplets represent the control-flow structures needed to iterate over any given datastructure, or multiple datastructures simultaneously. 
%
In particular, looplets are good at lifting code to the highest loop level that it's needed and subdividing iteration hierarchically in coordinate space.
%
Because looplets are compiled with progressive lowering, structure-specific mathematical optimizations such as integrals, multiply by zero, etc. can be implemented using simple compiler passes like term rewriting and constant propagation during the intermediate lowering stages.

The looplets are described in Figure~\ref{fig:looplets}. We simplify the presentation to focus on the semantics, rather than precise implementation. Several looplets introduce or modify variables in the scope of the target language. It is assumed that if a looplet introduces a variable to be used in a child looplet, the child looplet will not modify that variable. For more background on Looplets, we recommend the original work \cite{ahrens_looplets_2023}.

@@

>>>>

@@

\section{Background}

\subsection{Looplets}
Finch represents iteration patterns using Looplets, a language that decomposes datastructure iterators hierarchically. 
%
Looplets represent the control-flow structures needed to iterate over any given datastructure, or multiple datastructures simultaneously. 
%
In particular, looplets are good at lifting code to the highest possible loop level and subdividing iteration hierarchically in coordinate space.
%
Because looplets are compiled with progressive lowering, structure-specific mathematical optimizations such as integrals, multiply by zero, etc. can be implemented using simple compiler passes like term rewriting and constant propagation during the intermediate lowering stages.

The looplets are described in Figure~\ref{fig:looplets}. We simplify the presentation to focus on the semantics, rather than precise implementation. Several looplets introduce or modify variables in the scope of the target language. It is assumed that if a looplet introduces a variable, the child looplet will not modify that variable. For more background on Looplets, we recommend the original work \cite{ahrens_looplets_2023}.

### 2024-04-05 sections/tensors.tex
small fixes

Additionally, prior fiber-tree representations
focus on sparsity (where only the nonzero elements are represented) and treat
sparse vectors as sets of represented points. Since our fiber-tree
representation must handle other kinds of structure, such as diagonal,
repeated, or constant values, we generalize the concept to view each fiber as a mapping from
indices into a space of subfibers.

>>>>

Additionally, prior fiber-tree representations focus on sparsity (where only the nonzero elements are represented) and treat sparse vectors as sets of represented points. Since our fiber-tree representation must handle other kinds of structure, such as diagonal, repeated, or constant values, we generalize our fiber abstraction to allow arbitrary mappings from indices into a space of subfibers.
